Design of Adaptive Constellations and Error Protection Coding for Wireless Network Coding in 5-node Butterfly Networks

### 2017-05-29 Const_design.tex
Finished section 7.4 (to internal review)

\subsubsection{Reference Three-Step Scenarios}\label{Sec:Reference-3step-models}
The first scenario both sources again transmit their information one by one, but the relay is
allowed to combine the received (fully decoded) data packets into the network coded packet
$f(d_{A},d_{B})=d_{A}\oplus d_{B}$ and HSI channels are necessary to retrieve the desired
information at both sources, that is the traditional network coding approach (see Figure
\ref{fig:CTUpp_ref3stepNC}).

In the scenario is equivalent to a conventional routing, where the sources subsequently transmit
their data packet towards the relay. Relay then sends a complete source information (no NC coding is
applied) and thus the HSI channels are completely ignored (see Figure \ref{fig:CTUpp_ref3stepRouting}).

@@

\subsubsection{Numerical Results}
Within this experiment, we evaluated on our USRP platform the following situations:
\begin{itemize}
  \item The proposed adaptive constellation design from Section \ref{sub:Maximal-Throughput-of} 
  with optimized tuple ($r_b, r_s, N_b, N_s$) for each measured point
  (HW-pre-rotation on).
  \item The proposed adaptive constellation design with violated assumptions (pre-rotation off)
  \item Both 3-step reference scenarios introduced in Section \ref{Sec:Reference-3step-models}.
  \item Fundamental theoretical limits for the conventional reference 3-step scenarios.
\end{itemize}

We considered two setups:
\begin{itemize}
  \item Strong HSI and equal MA and BC. This scenario is suited for standard wireless network
  coding, because it can efficiently utilize the strong HSI channel. See Figure
  \ref{fig:CTUpp_comparison-schemaa} for the corresponding result. As one can see, the proposed
  framework significantly outperforms both reference 3-step scenarios as well the corresponding
  theoretical limits even if the pre-rotation is off! The bottleneck for the 3-step routing is BC
  channel, because it needs to pass twice amount of data from relay to destinations compared to
  all other schemes. The 3-step NC approach does not suffer from this and therefore its performance
  is a bit better, nevertheless we pay for orthogonality in the MA stage. The proposed performance
  of the proposed framework is superior to both reference models.
  \item Strong BC channel refers (among others) to a case with high relay power. The result is shown
  in Figure \ref{fig:CTUpp_comparison-schemab}. The 3-step routing works much better compared to the previous
  case, because of the strong BC channel. The conventional 3-step network coding suffers from weak
  HSI channel. The proposed design again significantly outperforms both reference 3-step scenarios.
  We should stress, that the performance gain is also caused by a \emph{partial usage} of the weak
  HSI channel.
\end{itemize}

\begin{figure}
\begin{centering}
\includegraphics[width=0.75\columnwidth]{fig/scheme_a}
\par\end{centering}
\centering{}\caption{Performance comparison for the setup
$\gamma_{\mathrm{BC}}\approx\gamma_{\mathrm{MAC}}$ and
$\gamma_{\mathrm{HSI}}\approx\gamma_{\mathrm{MAC}}$+3dB
.\label{fig:CTUpp_comparison-schemaa}}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.75\columnwidth]{fig/scheme_b}
\par\end{centering}
\centering{}\caption{Performance comparison for the setup
$\gamma_{\mathrm{BC}}\approx\gamma_{\mathrm{MAC}}$+5dB and
$\gamma_{\mathrm{HSI}}\approx\gamma_{\mathrm{MAC}}$-1dB
.\label{fig:CTUpp_comparison-schemab}}
\end{figure}

>>>>

\subsubsection{Reference Three-Step Scenarios}\label{Sec:Reference-3step-models}
In the first scenario both sources transmit their information one by one, but the relay is
allowed to combine the received (fully decoded) data packets into the network coded packet
$f(d_{A},d_{B})=d_{A}\oplus d_{B}$ and HSI channels are necessary to retrieve the desired
information at both sources, that is the traditional network coding approach (see Figure
\ref{fig:CTUpp_ref3stepNC}).

The second scenario is equivalent to a conventional routing, where the sources subsequently transmit
their data packet towards the relay. Relay then sends a complete source information (no NC coding is
applied) and thus the HSI channels are completely ignored (see Figure \ref{fig:CTUpp_ref3stepRouting}).

@@

\subsubsection{Numerical Results}
Within this experiment, we evaluated the following situations on our \emph{USRP platform}:
\begin{itemize}
  \item The proposed adaptive constellation design from Section \ref{sub:Maximal-Throughput-of} 
  with based on the optimized tuple ($r_b, r_s, N_b, N_s$) for each measured point
  (HW-pre-rotation on).
  \item The proposed adaptive constellation design with violated assumptions (pre-rotation off).
  \item Both 3-step reference scenarios introduced in Section \ref{Sec:Reference-3step-models}.
  \item Fundamental theoretical limits for the conventional reference 3-step scenarios.
\end{itemize}
In all measured cases, we manually selected the tuple maximizing the throughput. Our starting
point was the theoretical analysis, but this analysis does not take into account the imperfect
channel code and available discrete channel code rates (0.4, 0.5, \dots, 0.9). We also considered
$N_b
\le 2$, $N_s \le 1$ for simplicity\footnote{The higher order strategies like $(N_b=4, N_s=0)$
performed similarly as considered $(N_b=2, N_s=1)$ in our simulations. Note that much stronger
solution based
on the modulo-sum channel coding and wireless network coding function is available
\cite{Prochazka-2016}, nevertheless implementation of the 
non-binary channel code suitable for the USRP is challenging.}.

We considered two setups:
\begin{itemize}
  \item Strong HSI and equal MA and BC. This scenario is suited for standard wireless network
  coding, because it can efficiently utilize the strong HSI channel. See Figure
  \ref{fig:CTUpp_comparison-schemaa} for the corresponding result. As one can see, the proposed
  framework significantly outperforms both reference 3-step scenarios as well the corresponding
  theoretical limits even if the pre-rotation is off! The bottleneck for the 3-step routing is BC
  channel, because it needs to pass twice amount of data from relay to destinations compared to
  all other schemes. The 3-step NC approach does not suffer from this and therefore its performance
  is a bit better, nevertheless we pay for orthogonality in the MA stage. The performance
  of the proposed framework is superior to both reference models.
  \item Strong BC channel refers (among others) to a case with high relay power. The result is shown
  in Figure \ref{fig:CTUpp_comparison-schemab}. The 3-step routing works much better compared to the previous
  case, because of the strong BC channel. The conventional 3-step network coding suffers from weak
  HSI channel. The proposed design again significantly outperforms both reference 3-step scenarios.
  We should stress, that the performance gain is also caused by a \emph{partial usage} of the weak
  HSI channel.
\end{itemize}

The saturation of the reference 3-step strategies for high SNRs is a consequence of weaker
performance of the underlaying channel code, where the rate of the code is adjusted by means of
puncturing technique.

\begin{figure}
\begin{centering}
\includegraphics[width=0.75\columnwidth]{fig/scheme_a}
\par\end{centering}
\centering{}\caption{Performance comparison for the setup
$\gamma_{\mathrm{BC}}\approx\gamma_{\mathrm{MAC}}$ and
$\gamma_{\mathrm{HSI}}\approx\gamma_{\mathrm{MAC}}$+3dB. The numbers in boxes correspond with a
particular values (first row:$(N_b, r_b)$, second row:$(N_s, r_s)$) 
achieving a given maximal throughput. 
\label{fig:CTUpp_comparison-schemaa}}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.75\columnwidth]{fig/scheme_b}
\par\end{centering}
\centering{}\caption{Performance comparison for the setup
$\gamma_{\mathrm{BC}}\approx\gamma_{\mathrm{MAC}}$+5dB and
$\gamma_{\mathrm{HSI}}\approx\gamma_{\mathrm{MAC}}$-1dB.
The numbers in boxes correspond with a
particular values (first row:$(N_b, r_b)$, second row:$(N_s, r_s)$)
achieving a given maximal throughput.
\label{fig:CTUpp_comparison-schemab}}
\end{figure}
